Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-02-10 ms.tex
I added a few figures to describe why there was a local min for very large particle radii and how I excluded local min.

>>>>

On closer inspection, I see that there is a local minimum for large particle radii where the $\chi^2$ begins to increase from 3~$\mu$m to 2$\mu$m.
This is illustrated in Figure \ref{fig:localMinLargeRadii}.
\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{local_min_illustration.pdf}
\caption{A set of example Mie scattering models for example parameters for the Amplitude offset and median particle radius written as [A,r]. The model at 2~$\mu$m is slightly worse than at 3~$\mu$m, so it traps a few walkers in the MCMC run.}\label{fig:localMinLargeRadii}
\end{centering}
\end{figure}

When I discard walkers with very low likelihood, as done in CHIMERA, the local minima are not included since their so low probability.
The resulting MCMC run is shown in Figure \ref{fig:localMinExcludeCorner}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{corner_lognormal_mie_no_lmin.pdf}
\caption{MCMC fit when discarding points with a $\chi^2$ more than 5 times the minimum to exclude walkers that were trapped at local minima.}\label{fig:localMinExcludeCorner}
\end{centering}
\end{figure}
